    \documentclass[11pt,
        usenames, % allows access to some tikz colors
        dvipsnames % more colors: https://en.wikibooks.org/wiki/LaTeX/Colors
    ]{article}
    \usepackage[numbers]{natbib}
    \usepackage{
        amsmath,
        amssymb,
        fouriernc,
        fancyhdr, % page styling
        lastpage, % footer fanciness
        hyperref, % various links
        setspace, % line spacing
        amsthm, % newtheorem and proof environment
        mathtools, % \Aboxed for boxing inside aligns, among others
        float, % Allow [H] figure env alignment
        enumerate, % Allow custom enumerate numbering
        graphicx, % allow includegraphics with more filetypes
        wasysym, % \smiley!
        upgreek, % \upmu for \mum macro
        listings, % writing TrueType fonts and including code prettily
        tikz, % drawing things
        times,
        booktabs % \bottomrule instead of hline apparently
    }
    \usepackage[margin=0.8in, top=1in, bottom=1in]{geometry} % page geometry
    \usepackage[
        labelfont=bf, % caption names are labeled in bold
        font=scriptsize % smaller font for captions
    ]{caption}
    \usepackage[font=scriptsize]{subcaption} % subfigures

    \newcommand*{\scinot}[2]{#1\times10^{#2}}
    \newcommand*{\bra}[1]{\left<#1\right|}
    \newcommand*{\ket}[1]{\left|#1\right>}
    \newcommand*{\dotp}[2]{\left<#1\,\middle|\,#2\right>}
    \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
    \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
    \newcommand*{\rtd}[2]{\frac{\mathrm{d}^2#1}{\mathrm{d}#2^2}}
    \newcommand*{\ptd}[2]{\frac{\partial^2 #1}{\partial#2^2}}
    \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
    \newcommand*{\norm}[1]{\left|\left|#1\right|\right|}
    \newcommand*{\abs}[1]{\left|#1\right|}
    \newcommand*{\pvec}[1]{\vec{#1}^{\,\prime}}
    \newcommand*{\svec}[1]{\vec{#1}\;\!}
    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
    \newcommand*{\expvalue}[1]{\left<#1\right>}
    \newcommand*{\ang}[0]{\text{\AA}}
    \newcommand*{\mum}[0]{\upmu \mathrm{m}}

    \newtheorem{theorem}{Theorem}[section]

    \let\Re\undefined
    \let\Im\undefined
    \DeclareMathOperator{\Res}{Res}
    \DeclareMathOperator{\Re}{Re}
    \DeclareMathOperator{\Im}{Im}
    \DeclareMathOperator{\Log}{Log}
    \DeclareMathOperator{\Arg}{Arg}
    \DeclareMathOperator{\Tr}{Tr}
    \DeclareMathOperator{\E}{E}
    \DeclareMathOperator{\Var}{Var}
    \DeclareMathOperator*{\argmin}{argmin}
    \DeclareMathOperator*{\argmax}{argmax}
    \DeclareMathOperator{\sgn}{sgn}
    \DeclareMathOperator{\diag}{diag}

    \tikzstyle{circ} % usage: \node[circ, placement] (label) {text};
        = [draw, circle, fill=white, node distance=3cm, minimum height=2em]
    \definecolor{commentgreen}{rgb}{0,0.6,0}
    \lstset{
        basicstyle=\ttfamily\footnotesize,
        frame=single,
        numbers=left,
        showstringspaces=false,
        keywordstyle=\color{blue},
        stringstyle=\color{purple},
        commentstyle=\color{commentgreen},
        morecomment=[l][\color{magenta}]{\#}
    }

\begin{document}

\def\Snospace~{\S{}} % hack to remove the space left after autorefs
\renewcommand*{\sectionautorefname}{\Snospace}
\renewcommand*{\subsectionautorefname}{\Snospace}
\renewcommand*{\appendixautorefname}{\Snospace}
\renewcommand*{\figureautorefname}{Fig.}
\renewcommand*{\equationautorefname}{Eq.}
\renewcommand*{\tableautorefname}{Tab.}

\setstretch{1.2}

% helpful links:
% http://www.alexhunterlang.com/nsf-fellowship#TOC-Examples-of-Successful-Essays

\title{Nonlinear Tidal Dissipation in White Dwarfs}
\author{Yubo Su}
\date{}

\maketitle

\section{Introduction: White Dwarf Binaries}

White dwarfs (WDs) are remnants of stellar evolution for stars with mass
$\lesssim 8 M_{sun}$. They are some of the densest objects in the universe,
fitting a solar mass into an Earth-sized sphere. They are supported against
gravity by electron degeneracy pressure, a quantum mechanical effect arising from
subjecting electrons to immense pressures Furthermore, they exhibit various
chemical compositions, each of which is subject to different physics, and are
found in a variety of interesting systems. As such, WDs are a unique and diverse
window into matter under extreme conditions.

WDs are commonly found in binaries in which two objects orbit their center of
mass under mutual gravitational attraction. The companion object ranges
from another WD to a supermassive BH (SMBH), hypothesized to be at the center of
galaxies and have mass $\gtrsim 10^5$ solar masses. All of these binary systems
are very important to astrophysics. WD-WD binaries are most important for being
thought to generate \emph{Type Ia supernovae} in which two WDs merge and
initiate runaway thermonuclear fusion that powers an explosion, releasing
immense amounts of energy. Because Type Ia supernovae (SNe Ia) are highly
luminous, can be seen at large distances and are very consistent, they have been
used as a ``standard candle'' to probe the expansion rate of the universe (e.g.\
observations of SNe Ia provided the first evidence of the existence of dark
energy in the universe).

WD-BH systems are also interesting subjects of study. Recent works indicate that
as WDs plunge close to BHs, they will produce observable flares induced by
gravitational tidal forces\cite{flares}. A WD orbiting a SMBH would also produce
gravitational waves, waves of space-time warping as predicted by Einstein's
theory of general relativity, that are expected to be detected by the
space-based \emph{Laser Interferometer Space Antenna (LISA)} when
deployed\cite{lisa}. Gravitational wave astronomy is an increasingly exciting
field as the \emph{Laser Interferometer Gravitational-Wave Observatory (LIGO)}
continues to make progress since its first detection in late 2015. As
gravitational wave astronomy relies on accurate predictions of the expected
signals, it is important to build as accurate models as possible before
observation runs begin.

\subsection{Tidal Dissipation}

The excitation of \emph{internal gravity waves} in the WD by the tidal forces of
the companion is an effect exhibited in all of the aforementioned systems.
Internal gravity waves, not to be confused with the gravitational waves above,
are internal displacements in the WD fluid that oscillate and propagate due to a
restoring buoyancy force. These tidally excited gravity waves are analogous to
tides on Earth raised by the Moon and the Sun, except that since WDs do not have
sharp surfaces these waves are internal to the WD\@. As these waves propagate
outward from where they are excited, they are expected to grow in amplitude
until they break, as do ocean waves on a shore, and deposit both energy and
angular momentum in the WD envelope.

Previous work predicts that this dissipation mechanism can generate
significantly more energy than thermal radiation from the WD surface alone and
are thus a significant contribution to the WD energy budget\cite{fullerII}. The
exact radial dissipation profile is of interest since it both is sensitive to WD
properties and can produce vastly different observable outcomes. One proposed
outcome is a \emph{tidal nova}, in which heating in the WD's degenerate hydrogen
layer is sufficient to trigger runaway nuclear fusion and an observable
surface explosion\cite{tidal_novae}. Understanding whether such phenomena occur
requires understanding how energy is distributed internally inside a WD\@.

Internal gravity wave breaking is a nonlinear hydrodynamic phenomenon. Such
phenomena are known to require numerical simulation to study. It is therefore
paramount to begin numerical study to build dissipation models inside WDs to
characterize what phenomena can be observed in different WD models.

\section{Proposed Research}

\textbf{We propose to study tidal dissipation via nonlinear gravity wave
breaking in white dwarfs using numerical simulation.}

Our research will initially consist of numerically computing for various WD
models and compositions the energy and angular momentum dissipation profiles
inside WDs. Once such profiles are obtained, we intend to add these profiles to
existing stellar evolution codes to study the dynamical effects of tidal
dissipation. We will attempt to find a compact or even analytical representation
of our numerical work to greatly simplify and accelerate such integration.
Finally, we will make observational predictions with our results and compare our
predictions with existing observed WDs in binaries. Any software and results
would be made in accordance with best practice and publicly available for the
scientific community.

\subsection{Numerical Approach}

Much of our proposed research will rely on numerical solutions to fluid
dynamical equations. Guided by current literature, we have begun with the
Dedalus numerical solver, a modern spectral solver that integrates the fluid
equations both quickly and to high accuracy\cite{dedalus}. Dedalus has been
shown in current literature to describe turbulence and fluid instabilities well,
and our preliminary work supports this conclusion.

For our problem, we will first adapt Dedalus to study gravity waves in the
stratified atmosphere/envelope of WDs and later consider global (spherical) WD
models. Should Dedalus prove inadequate, we are able (\autoref{ss:quals}) and
willing to contribute a new hydrodynamic code to the community. Notably, no
GPU-accelerated spectral hydrodynamic code has yet been released, which would be
of great value to researchers. Nevertheless, in the interest of the proposed
science objectives codes will be developed on an as-needed basis.

After characterizing tidal dissipation, we intend to apply our models to WD
evolution under tidal heating. Modules for Experiments in Stellar Astrophysics
(MESA) is a proven stellar evolution code that would require comparatively
little adaptation to incorporate tidal heating in studying WD
evolution\cite{MESA}. A released extension to MESA containing our work would be
the most effective way to release our work to prospective users.

\subsection{Qualifications}\label{ss:quals}

The proposing researcher (YS) and his adviser (DL) are uniquely qualified to
pursue such studies. YS has completed a double Bachelors degree in physics and
computer science from the California Institute of Technology. He also has ample
research experience in numerical simulation and is continuing to pursue academic
study in hydrodynamics, turbulence and computation. Finally, he has worked in
the software industry for a year and continues to follow discussions of best
practice far ahead of those in academia and apply them to his own work.

DL is a co-author of a number of recent papers on WD binaries and is an
expert on many related subjects such as fluid dynamics in extreme matter and
studies of other compact object systems. Cornell University also houses Saul
Teukolsky's research group, one of the pre-eminent numerical relativity groups
in the world, which will be frequently consulted for numerical best practices.

\subsection{Applications, Interest to the DoD}

Although our proposed research deals with astronomical objects and phenomena
(WDs and BHs), the tools we use and develop in our research
have applications in many areas of physical sciences and engineering. As
discussed above, through our research we will develop extensive expertise in
nonlinear hydrodynamics (internal gravity waves), radiation physics (radiative
transfer and diffusion of heat inside WD), nuclear physics (tidal heating
leading to runaway fusion) and numerical computation. Such a research project
thus contributes to many science and engineering fields and equips me to tackle
an exceptionally large variety of problems.

The proposed research is extremely relevant to Department of Defense (DoD)
fields of interest. WDs and its energetic phenomena we propose to study (e.g.\
novae) of all sorts are natural laboratories of extreme physics that have
direct consequences for understanding of plasmas and other technologies integral
to propulsion in aeronautics. A theory of nonlinear wave breaking would have
far-reaching consequences in turbulence study and atmospheric sciences. Finally,
the observation of our predictions could shed light on atmospheric optics,
whether as a use for calibration or understanding contamination effects.

\bibliographystyle{plainnat}
\renewcommand{\bibname}{References}
{\scriptsize \bibliography{proposal}}

\end{document}

